Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
Self-review

	\ALG performs at least one swap for every expansion of a ground set.
	Each expansion reduces the number of isolated nodes by $1$ or $2$.
	The decrease of two isolated nodes occurs when the largest component on the initial cluster of $x_i$ is still a trivial component; this can occur at most $\ell$ times.
	We start with $k \cdot \ell - (k-1)$ isolated nodes (a~single $k-1$ ground set is revealed prior to $\{x_0, y_0\}$), and we end with isolated $\ell+1$ nodes.
	Hence, the total number of swaps of \ALG is at least $k\cdot \ell - k - 2 \ell$.
	The competitive ratio is then $\ALG / \OPT \geq (k\cdot \ell - k - 2\ell) / 2$.
\end{proof}

@@

	%Let $A^I$ be the cost of (extra-cluster) communication incurred in this phase by \TAlg between pairs that belonged to the single component at the end of the phase.
	%Let $A^E$ be the cost of (extra-cluster) communication incurred in this phase between the nodes that belong to different components at the end of this phase.
	Let $\TAlg(M)$ be the cost of migrations performed by \TAlg in this phase.
	\TAlg performs at most $2 \ell$ component merge operations, as
	exceeding this number means that a component of size $4$ exists, and the phase should have ended already.
	Combining this with Lemma~\ref{lem:1req} gives us $\TAlg(M) \leq 8\alpha\cdot\ell$ (recall that an exchange costs $2\alpha$).
	%Together with Lemma~\ref{lem:1req}, this allows us to bound the cost of migrations, $\TAlg(M) \leq 6\cdot\alpha\cdot\ell$.

	Now we bound $\TAlg(\sigma_I)$.
	A~cluster of type $C_3$ contributes at most $3 \alpha - 1$ to $\TAlg(\sigma_I)$, as two pairs of nodes from the component are saturated and contribute $\alpha$ each, and the third, unsaturated pair contributes at most $\alpha-1$.
	Other cluster types contribute less: $C_1$ contributes~$0$ and $C_2$ contributes $\alpha$.
	Summing this over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.

>>>>

	\ALG performs at least one swap for every expansion of a ground set.
	Each expansion reduces the number of isolated nodes by $1$ or $2$.
	The decrease of two isolated nodes occurs when the largest component on  $I(x_i)$ is still trivial; this occurs at most $\ell$ times.
	We start with $k \cdot \ell - (k-1)$ isolated nodes (a~single $k-1$ ground set is revealed prior to $\{x_0, y_0\}$), and we end with isolated $\ell+1$ nodes.
	Hence, the total number of swaps of \ALG is at least $k\cdot \ell - k - 2 \ell$.
	The competitive ratio is then $\ALG / \OPT \geq (k\cdot \ell - k - 2\ell) / 2$.
\end{proof}

@@

	%Let $A^I$ be the cost of (extra-cluster) communication incurred in this phase by \TAlg between pairs that belonged to the single component at the end of the phase.
	%Let $A^E$ be the cost of (extra-cluster) communication incurred in this phase between the nodes that belong to different components at the end of this phase.
	Let $\TAlg(M)$ be the cost of migrations performed by \TAlg in this phase.
	\TAlg performs at most $2 \ell$ component merge operations ---
	exceeding this number would mean that a~component of size $4$ exists, and the phase should have ended already.
	We bound the cost of a each repartition by Lemma~\ref{lem:1req}, to obtain $\TAlg(M) \leq 8\alpha\cdot\ell$.
	%Together with Lemma~\ref{lem:1req}, this allows us to bound the cost of migrations, $\TAlg(M) \leq 6\cdot\alpha\cdot\ell$.

	Now we bound $\TAlg(\sigma_I)$.
	A~cluster of type $C_3$ contributes at most $3 \alpha - 1$ to $\TAlg(\sigma_I)$, as two pairs of nodes from the component are saturated and contribute $\alpha$ each, and the third, unsaturated pair contributes at most $\alpha-1$.
	Other cluster types contribute less: $C_1$ contributes~$0$ and $C_2$ contributes $\alpha$.
	Summing over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.
